---
title: "R Notebook"
output: html_notebook
---
generate three data frames corresponding to copy number 1 2 3. (python)
only select corrected logR of cells within mapD range.
```{r}
library(ggplot2)
```

```{r}
getwd()
data_cn1 = read.table("/Users/Yibing/Bioinfo-Master-Thesis/Data/combined_logR_corrected_cn123/cn1.txt", sep = "\t", header = FALSE)[4]
colnames(data_cn1) = "logR"
data_cn1

data_cn2 = read.table("/Users/Yibing/Bioinfo-Master-Thesis/Data/combined_logR_corrected_cn123/cn2.txt", sep = "\t", header = FALSE)[4]
colnames(data_cn2) = "logR"
data_cn2

data_cn3 = read.table("/Users/Yibing/Bioinfo-Master-Thesis/Data/combined_logR_corrected_cn123/cn3.txt", sep = "\t", header = FALSE)[4]
colnames(data_cn3) = "logR"
data_cn3



median(unlist(data_cn1))
median(unlist(data_cn2))
median(unlist(data_cn3))
```


```{r}
boxplot_cn1 = boxplot(data_cn1)
boxplot_cn2 = boxplot(data_cn2)
boxplot_cn3 = boxplot(data_cn3)


data_cn1_no_outliers["logR"] = as.data.frame(data_cn1$logR[data_cn1$logR>boxplot_cn1$stats[1] & data_cn1$logR<boxplot_cn1$stats[5]])
data_cn2_no_outliers["logR"] = as.data.frame(data_cn2$logR[data_cn2$logR>boxplot_cn2$stats[1] & data_cn2$logR<boxplot_cn2$stats[5]])
data_cn3_no_outliers["logR"] = as.data.frame(data_cn3$logR[data_cn3$logR>boxplot_cn3$stats[1] & data_cn3$logR<boxplot_cn3$stats[5]])

boxplot(data_cn1_no_outliers$logR)
boxplot(data_cn2_no_outliers$logR)
boxplot(data_cn3_no_outliers$logR)
```





plot logR corresponding to CN1 CN2 CN3
```{r}
library(ggplot2)
```

```{r}
plot_cn1 = ggplot(data_cn1, aes(logR)) + geom_histogram(binwidth = 0.1) +  labs(x = "logR_cn1", y = "density", color = NULL)
print(plot_cn1)

plot_cn2 = ggplot(data_cn2, aes(logR)) + geom_histogram(binwidth = 0.1)+  labs(x = "logR_cn2", y = "density", color = NULL)
print(plot_cn2)

plot_cn3 = ggplot(data_cn3, aes(logR)) + geom_histogram(binwidth = 0.1) +  labs(x = "logR_cn3", y = "density", color = NULL) + 
print(plot_cn3)
```

ln(result.normalised/median)
```{r}
library(fitdistrplus)
#descdist(data_cn2$logR, discrete = FALSE, boot = 100)

fit_cn1 = fitdist(data_cn1_no_outliers$logR, "norm") #normal
fit_cn2 = fitdist(data_cn2_no_outliers$logR, "norm") #normal
fit_cn3 = fitdist(data_cn3_no_outliers$logR, "norm") #normal

summary(fit_cn1)
summary(fit_cn2)
summary(fit_cn3)
```
```{r}
print("CN1 estimate paramaters")
fit_cn1$estimate

print("CN2 estimate paramaters")
fit_cn2$estimate

print("CN3 estimate paramaters")
fit_cn3$estimate
```









###########################################################################################
using bin reads will involve cell specific effects to the system
broaden the distribution --> leads to overlapping --> worse parameters for stimulation later
##################################################
bin reads
```{r}
embryoNumber = c(1,2,3,4,5,6,7,8,9,
                 10,11,12,13,14,15,16,17,18,19,
                 20,21,22,23,24,25,26,27,28,29,
                 30,31,32,33,34,35,36,37,38,39,
                 40,41,42,43,44,45,46,47)
cellNumber = list(c(1),c(1),c(1,2),c(1,2),c(1),c(1,2,3),c(1,2),c(1,2,3),c(2,3),
                  c(2,4),c(2,3,4,6,7,9,10),c(1,2,4,7),c(1), c(3,5,6),c(1,2,3),c(1,4),c(2,3,5,7,8,9,10),c(1,2,3,4,5,6,7,8,9,11,12),c(2),
                  c(1,2,3),c(2,3),c(1,2),c(1),c(1,2,3),c(1,2,3,4),c(3,4,5),c(1,2,3,5),c(1,2),c(1,4),
                  c(1,2,3,4),c(1),c(3,4,5,6,7,8,9),c(1,2,3,4,5,6,7,8,9,11,12),c(2),c(1,2,3,4),c(1),c(1,2),c(1,2,3,4),c(1,2),
                  c(7,8,9,10,11,12,13,14,15,17,18,19,21,22,24,25),c(1,2,3,4,5,6,7),c(1,2,3,4,5,7,8),c(1,2,3,4,5,6),c(1,2,4,5,6,7,8,9,10,11,13,14,15,16,17,18,22,24,25,26,28,29,31,32,33,35,36,37,38,39),c(1,2,4,5,8,9,10,11,12,13),c(2,3,5,6,7,8,9,10,11,12,13,15,16,17,18,21,22),c(15,16,17,18,20,21,22,23,24,25,26,27,28,29,30))

data_cn1_reads = data.frame()
data_cn2_reads = data.frame()
data_cn3_reads = data.frame()

for (i in 1:length(embryoNumber)){
  for (n in 1:length(as.numeric(unlist(cellNumber[i])))){
    rawFileName = paste(paste(paste("/Users/Yibing/Bioinfo-Master-Thesis/Data/raw_counts/TVEMB", (embryoNumber[i])[1], sep = ""), (unlist(cellNumber[i]))[n], sep = "_"), "250K.101.sorted.count-t", sep = ".")  
    raw_data = read.table(rawFileName, sep = "\t", header = FALSE)
    raw_data = raw_data[c(1,2,3,6)]
    colnames(raw_data) = c("chr", "start", "end", "reads")
    cnFileName = paste(paste(paste("/Users/Yibing/Bioinfo-Master-Thesis/Data/logr_cn_per_bin/TVEMB", (embryoNumber[i])[1], sep = ""), (unlist(cellNumber[i]))[n], sep = "_"), "250K.101.sorted.count.gamma_15.gc_corrected.segments.copynumber.txt", sep = ".")  
    cn_data = read.table(cnFileName, sep = "\t", header = TRUE)
    cn_data = cn_data[c(1,2,3,5)]
    data = merge(raw_data, cn_data)
    data_cn1_reads = rbind(data_cn1_reads,subset(data, CN_segment == "1"))
    data_cn2_reads = rbind(data_cn2_reads,subset(data, CN_segment == "2"))
    data_cn3_reads = rbind(data_cn3_reads,subset(data, CN_segment == "3"))
  }
}

dim(data_cn1_reads)
dim(data_cn2_reads)
dim(data_cn3_reads)
```

plot reads density corresponding to copy number 1 2 3
```{r}
plot_cn1 = ggplot(data_cn1_reads, aes(reads)) +
  geom_density() +
  xlim(0,1500) +
  labs(x = "cn1_reads", y = "density", color = NULL) 
print(plot_cn1)

plot_cn2 = ggplot(data_cn2_reads, aes(reads)) + 
  geom_density() +
  xlim(0,1500) +
  labs(x = "cn2_reads", y = "density", color = NULL) 
print(plot_cn2)

plot_cn3 = ggplot(data_cn3_reads, aes(reads)) + 
  geom_density() +  
  xlim(0,1500) +
  labs(x = "cn3_reads", y = "density", color = NULL) 
print(plot_cn3)

```

```{r}
library(fitdistrplus)

descdist(data_cn1_reads$reads, discrete = TRUE, boot = 500)
fit_cn1 = fitdist(data_cn1_reads$reads, "pois")
summary(fit_cn1)
denscomp(list(fit_cn1))

descdist(data_cn2_reads$reads, discrete = TRUE, boot = 500)
fit_cn2 = fitdist(data_cn2_reads$reads, "pois")
summary(fit_cn2)
denscomp(list(fit_cn2))

descdist(data_cn3_reads$reads, discrete = TRUE, boot = 500)
fit_cn3 = fitdist(data_cn3_reads$reads, "pois")
summary(fit_cn3)
denscomp(list(fit_cn3))
```

```{r}
summary(fit_cn1)
#       estimate Std. Error
#lambda 63.74629 0.01802465
summary(fit_cn2)
#       estimate  Std. Error
#lambda 114.2031 0.007269994
summary(fit_cn3)
#       estimate Std. Error
#lambda   159.33 0.04413308


```